---
title: "Grain Boundaries Project"
output:
  html_document: 
    toc: true
    toc_float: true
    code_folding: hide
  html_notebook: default
---

## Libraries

```{r, message = F, warning = F}
knitr::opts_chunk$set(message = F, warning = F)
library(tidyverse)
library(yacca)
library(stringr)
jackyl_theme <- function() {
  theme_bw() +
  theme(axis.text = element_text(size = 10, color = "#04122A"),
        text = element_text(size = 12, face = "bold", color = "#04122A"),
        panel.grid.major = element_line(color = "#9ca5ac", linetype = 1),
        panel.grid.minor = element_line(color = "#9ca5ac", linetype = 2),
        panel.border = element_rect(color = "#1c68a6", size = 1.5),
        panel.background = element_rect(fill = "#dcddd9"),
        plot.background = element_rect(fill = "#f9f6f3"),
        legend.background = element_rect(fill = "#f9f6f3"),
        axis.title = element_text(size = 14, color = "#04122A"),
        axis.ticks.length = unit(1, "pt"))
}

```


**Data Files Needed**:

 * "GBE2.csv"
 * "fcc1-2.txt"
 * "fcc2-mobility.txt"
 
## Olmsted Dataset

```{r}
setwd("~/Desktop/Research/GrainBoundaries/") # Set to working directory with data files

mobility <- read_tsv("fcc2-mobility.txt", col_names = F, skip = 1)
colnames(mobility) <- c("GB Index", "Mobility (m/s - GPA)")
gbenergy <- read_csv("Ni-Al-Au-Cu_energies.csv", col_names = T, skip = 1)
data <- read_csv('GBE2.csv', col_names = T, col_types = cols())

```
 
```{r, echo=FALSE, fig.height=6, fig.width=6}

xcols <- c("mixed", "tilt", "twist", "dot_hkl", "min_theta", "max_theta")

for (y in c("ni1", "al", "au1", "mishin cu")) {
  ccaobj <- cca(x = data[,xcols], y = data[,y])
  # helio.plot(ccaobj, main = y)
}

```

```{r}
Olmsted <- read_fwf('fcc1-2.txt', col_positions = fwf_widths(30))

## Remove GB_index Lines
index <- numeric(0)
for (i in 1:nrow(Olmsted)) {
  line <- Olmsted[i,]
  if (!is.na(line) && str_detect(line, "GB_index")) {
    index <- c(index, i)
  }
}
Olmsted <- Olmsted[-index,]

## Tabulate all the lines that follow a newline (NA)
## Takes advantage of structure in TXT
tabulatedVal <- matrix(ncol = 1)
for (j in 2:nrow(Olmsted)) {
  if (is.na(Olmsted$X1[j-1])) {
    tabulatedVal <- rbind(tabulatedVal, Olmsted$X1[j])
  }
}
tabulatedVal <- tabulatedVal[-1,]

## Normalizes Axis and Boundary Plane Normal 
## Output is Matrix with normalized values
output <- matrix(ncol = 5, nrow = length(tabulatedVal))
for (i in 1:length(tabulatedVal)) {
  rel <- c(1:3, 7, 9:11) # Relevant Indices
  temp <- as.numeric(str_split(tabulatedVal[i], " ")[[1]][rel]) # Split vector by space, pull relevant indices

  axisdist <- sqrt(temp[1]^2 + temp[2]^2 + temp[3]^2)
  bounddist <- sqrt(temp[5]^2 + temp[6]^2 + temp[7]^2)
  output[i,1] <- acos(temp[1] / axisdist) * 180 / pi
  output[i,2] <- acos(temp[2] / axisdist) * 180 / pi
  output[i,3] <- temp[4]
  output[i,4] <- acos(temp[5] / bounddist) * 180 / pi
  output[i,5] <- acos(temp[6] / bounddist) * 180 / pi
}

colnames(output) <- c("Axis1", "Axis2", "MisorDegrees", "NormBoundaryH", "NormBoundaryK")
#write_csv(x = as_tibble(output), path = "GB5DOF.csv")
```

## Canonical Correlation Analysis {.tabset}

### Mishin Copper 

```{r fig.width = 10, fig.height = 10}
CuGBEnergy <- gbenergy$`mishin cu`
CuCCAobj <- cca(x = cbind(output, mobility$`Mobility (m/s - GPA)`), y = CuGBEnergy)
helio.plot(CuCCAobj)
```

### Aluminum

```{r fig.width = 10, fig.height = 10}
AlGBEnergy <- gbenergy$al
AlCCAobj <- cca(x = output, y = cbind(AlGBEnergy, mobility$`Mobility (m/s - GPA)`))
helio.plot(AlCCAobj)
```

### Gold

```{r fig.width = 10, fig.height = 10}
AuGBEnergy <- gbenergy$au1
AuCCAobj <- cca(x = output, y = cbind(AuGBEnergy, mobility$`Mobility (m/s - GPA)`))
helio.plot(AuCCAobj)
```

### Nickel

```{r fig.width = 10, fig.height = 10}
NiGBEnergy <- gbenergy$ni1
NiCCAobj <- cca(x = output[,1:5], y = cbind(NiGBEnergy))
helio.plot(NiCCAobj)
```


## Random Forest Attempt {.tabset}

```{r}
library(randomForest)

randForestObj <- randomForest(CuGBEnergy~Axis1+Axis2+MisorDegrees+NormBoundaryH+NormBoundaryK, data = output, ntree = 400)
importance(randForestObj)
print(randForestObj)
```


## Systematic RandomForests {.tabset}

### Single Importance Weights

```{r}
output <- as_tibble(output)
runRF <- function(DOFNum, data, GBEnergy) {
  obj <- randomForest(x = data[DOFNum],y = GBEnergy, ntree = 400)
  weights <- obj$importance
  maxWeight <- max(obj$importance)
  index <- which.max(obj$importance)
  return(c(rownames(weights)[index], maxWeight))
}

singletons <- matrix(ncol = 2)
for (DOF in 1:5) {
  singletons <- rbind(singletons, runRF(DOF, output, CuGBEnergy))
}

singletons <- as_tibble(singletons[-1,]) %>% mutate(Type = rep(1, 5))

```

### Pairwise Importance Weights

```{r}
pairs <- matrix(ncol = 2)
for (DOF in 1:5) {
  for (DOF2 in 1:5) {
    if (DOF >= DOF2) {
      next
    }
    pairs <- rbind(pairs, runRF(c(DOF, DOF2), output, CuGBEnergy))
  }
}

pairs <- as_tibble(pairs[-1,]) %>% mutate(Type = rep(2, 10))
```

### Triple Importance Weights

```{r}
triplets <- matrix(ncol = 2)
for (DOF in 1:5) {
  for (DOF2 in 1:5) {
    for (DOF3 in 1:5) {
      if ((DOF > DOF2) || (DOF2 > DOF3) || DOF == DOF2 || DOF2 == DOF3) {
        next
      }
      print(c(DOF, DOF2, DOF3))
      triplets <- rbind(triplets, runRF(c(DOF, DOF2, DOF3), output, CuGBEnergy))
    }
  }
}

triplets <- as_tibble(triplets[-1,]) %>% mutate(Type = rep(3, 10))
```

### Quadruple Importance Weights

```{r}
quad <- matrix(ncol = 2)
for (DOF in 1:5) {
  for (DOF2 in 1:5) {
    for (DOF3 in 1:5) {
      for (DOF4 in 1:5) {
        if ((DOF >= DOF2) || (DOF2 >= DOF3) || (DOF3 >= DOF4)) {
          next
        } 
        print(c(DOF, DOF2, DOF3, DOF4))
        quad <- rbind(quad, runRF(c(DOF, DOF2, DOF3, DOF4), output, CuGBEnergy))
      }
    }
  }
}

quad <- as_tibble(quad[-1,]) %>% mutate(Type = rep(4, 5))
```

### Penta Importance Weights

```{r}
val <- runRF(1:5, output, CuGBEnergy)
pents <- as_tibble(matrix(val, ncol = 2)) %>% mutate(Type = 5)

```

### Weight Analysis

```{r}
singletons[which.max(singletons$V2),]
pairs[which.max(pairs$V2),]
triplets[which.max(triplets$V2),]
quad[which.max(quad$V2),]
pents

Totals <- rbind(singletons, pairs, triplets, quad, pents) %>% mutate(V1 = as.factor(V1), 
                                                                     V2 = as.numeric(V2),
                                                                     Type = as.factor(Type))
```

### Visualization

```{r}
ggplot(Totals) + 
  geom_point(aes(x = V1, y = V2, color = Type)) +
  labs(x = "Degree of Freedom", 
       y = "Importance Weight", 
       title = "Importance Weights of Various DOF for Copper GB Energy") +
  jackyl_theme()
```

### Marginal Distributions

```{r}
library(gridExtra)
p1 <- ggplot(output) + geom_histogram(aes(x = Axis1)) +
        labs(x = "Rotation Axis 1 (Deg)",
               y = "Counts") +
        jackyl_theme()
p2 <- ggplot(output) + geom_histogram(aes(x = Axis2)) +
        labs(x = "Rotation Axis 2 (Deg)",
               y = "Counts") +
        jackyl_theme()
p3 <- ggplot(output) + geom_histogram(aes(x = MisorDegrees)) +
        labs(x = "Misorientation Angle (Deg)",
               y = "Counts") +
        jackyl_theme()
p4 <- ggplot(output) + geom_histogram(aes(x = NormBoundaryH)) + 
        labs(x = "Boundary Axis H (Deg)",
               y = "Counts") +
        jackyl_theme()
p5 <- ggplot(output) + geom_histogram(aes(x = NormBoundaryK)) +
        labs(x = "Boundary Axis K (Deg)",
               y = "Counts") +
        jackyl_theme()

grid.arrange(p1, p2, p3, p4, p5, ncol = 2)
```


### ChiSquared Test

```{r}
chisq.test(output$NormBoundaryH, output$NormBoundaryK)

```

## Rohrer Dataset

```{r}
library(readxl)
RohrerData <- read_excel("../gb_data-Rohrer.xlsx",
                       col_names = c("Ax1", "Ax2", "Ax3", "Ang", "n1", "n2", "n3", 
                                     "AusteniteEnergy", "AusteniteArea",
                                     "SrTiO3Energy", "SrTiO3Area",
                                     "FerriteEnergy", "FerriteArea",
                                     "NiEnergy", "NiArea",
                                     "AlArea", "CuInSe2Area",
                                     "SiArea"), skip = 1)

RohrerDOF <- select(RohrerData, Ax1, Ax2, Ang, n1, n2, 
                    AusteniteEnergy, SrTiO3Energy, FerriteEnergy,
                    NiEnergy) %>%
               mutate(Ax1 = acos(Ax1) * 180 / pi,
                      Ax2 = acos(Ax2) * 180 / pi,
                      n1 = acos(n1) * 180 / pi,
                      n2 = acos(n2) * 180 / pi)
```

## Canonical Correlation Analysis {.tabset}

### Austenite

```{r fig.width = 8, fig.height = 8}
ausObj <- cca(x = select(RohrerDOF, Ax1, Ax2, Ang, n1, n2), 
              y = RohrerDOF$AusteniteEnergy,
              xlab = c("Axis1", "Axis2", "MisorAngle", "NormH", "NormK"),
              ylab = "Austenite GB Energy")
helio.plot(ausObj)

```

### SrTiO3 

```{r fig.width = 8, fig.height = 8}
SrTiO3Obj <- cca(x = select(RohrerDOF, Ax1, Ax2, Ang, n1, n2), 
              y = RohrerDOF$SrTiO3Energy,
              xlab = c("Axis1", "Axis2", "MisorAngle", "NormH", "NormK"),
              ylab = "SrTiO3 GB Energy")
helio.plot(SrTiO3Obj)

```

### Ferrite

```{r fig.width = 8, fig.height = 8}
ferriteObj <- cca(x = select(RohrerDOF, Ax1, Ax2, Ang, n1, n2), 
              y = RohrerDOF$FerriteEnergy,
              xlab = c("Axis1", "Axis2", "MisorAngle", "NormH", "NormK"),
              ylab = "Ferrite GB Energy")
helio.plot(ferriteObj)

```

### Ni

```{r fig.width = 8, fig.height = 8}
NiObj <- cca(x = select(RohrerDOF, Ax1, Ax2, Ang, n1, n2), 
              y = RohrerDOF$NiEnergy,
              xlab = c("Axis1", "Axis2", "MisorAngle", "NormH", "NormK"),
              ylab = "Nickel GB Energy")
helio.plot(NiObj)

```


## Systematic RandomForests {.tabset}

### Single Importance Weights

```{r}
output <- as_tibble(RohrerDOF)
runRF <- function(DOFNum, data, GBEnergy) {
  obj <- randomForest(x = data[DOFNum],y = GBEnergy, ntree = 400)
  weights <- obj$importance
  maxWeight <- max(obj$importance)
  index <- which.max(obj$importance)
  return(c(rownames(weights)[index], maxWeight))
}

singletons <- matrix(ncol = 2)
for (DOF in 1:5) {
  singletons <- rbind(singletons, runRF(DOF, output, RohrerDOF$AusteniteEnergy))
}

singletons <- as_tibble(singletons[-1,]) %>% mutate(Type = rep(1, 5))

```

### Pairwise Importance Weights

```{r}
pairs <- matrix(ncol = 2)
for (DOF in 1:5) {
  for (DOF2 in 1:5) {
    if (DOF >= DOF2) {
      next
    }
    pairs <- rbind(pairs, runRF(c(DOF, DOF2), output,  RohrerDOF$AusteniteEnergy))
  }
}

pairs <- as_tibble(pairs[-1,]) %>% mutate(Type = rep(2, 10))
```

### Triple Importance Weights

```{r}
triplets <- matrix(ncol = 2)
for (DOF in 1:5) {
  for (DOF2 in 1:5) {
    for (DOF3 in 1:5) {
      if ((DOF > DOF2) || (DOF2 > DOF3) || DOF == DOF2 || DOF2 == DOF3) {
        next
      }
      print(c(DOF, DOF2, DOF3))
      triplets <- rbind(triplets, runRF(c(DOF, DOF2, DOF3), output,  RohrerDOF$AusteniteEnergy))
    }
  }
}

triplets <- as_tibble(triplets[-1,]) %>% mutate(Type = rep(3, 10))
```

### Quadruple Importance Weights

```{r}
quad <- matrix(ncol = 2)
for (DOF in 1:5) {
  for (DOF2 in 1:5) {
    for (DOF3 in 1:5) {
      for (DOF4 in 1:5) {
        if ((DOF >= DOF2) || (DOF2 >= DOF3) || (DOF3 >= DOF4)) {
          next
        } 
        print(c(DOF, DOF2, DOF3, DOF4))
        quad <- rbind(quad, runRF(c(DOF, DOF2, DOF3, DOF4), output,  RohrerDOF$AusteniteEnergy))
      }
    }
  }
}

quad <- as_tibble(quad[-1,]) %>% mutate(Type = rep(4, 5))
```

### Penta Importance Weights

```{r}
val <- runRF(1:5, output,  RohrerDOF$AusteniteEnergy)
pents <- as_tibble(matrix(val, ncol = 2)) %>% mutate(Type = 5)

```

### Weight Analysis

```{r}
library(forcats)
singletons[which.max(singletons$V2),]
pairs[which.max(pairs$V2),]
triplets[which.max(triplets$V2),]
quad[which.max(quad$V2),]
pents

Totals <- rbind(singletons, pairs, triplets, quad, pents) %>% 
            mutate(V1 = as.factor(V1), 
                   V2 = as.numeric(V2),
                   Type = as.factor(Type))
```

### Visualization

```{r}
Totals <- mutate(Totals, V1 = fct_recode(Totals$V1, "MisorDegrees" = "Ang",
                                         "Axis1" = "Ax1",
                                         "Axis2" = "Ax2",
                                         "NormBoundaryH" = "n1",
                                         "NormBoundaryK" = "n2"),
                  V1 = fct_relevel(Totals$V1, "Axis1", "Axis2", "MisorDegrees", "NormBoundaryH", "NormBoundaryK"))
ggplot(Totals) +
  geom_point(aes(x = V1, y = V2 , color = Type)) +
  labs(x = "Degree of Freedom", 
       y = "Importance Weight", 
       title = "Importance Weights of Various DOF for Austenite GB Energy") +
  jackyl_theme() 

```
